Research on vehicle-to-building (V2B) coordination requires datasets that
couple building electrical load, electric-vehicle (EV) charging sessions,
driver behavior, electricity tariffs, demand-response (DR) events, and
distributed energy resources on a common clock. Such data is largely
unavailable: real charging logs are privacy-restricted and confined to a small
number of sites, and no charging equipment records battery state of charge
(SoC), the quantity most V2B optimization methods schedule around. We present
\generator{}, a configurable generator that produces coupled fifteen-minute
V2B datasets for parameterized scenarios under three guarantees. First, the
building load is \emph{physically simulated}: each dataset is produced by an
EnergyPlus simulation of a DOE prototype building under a perturbed
typical-year weather realization, and the same weather drives the photovoltaic
model and is exported alongside the data. Second, driver behavior is
\emph{calibrated}: arrival, dwell, and energy-demand distributions are fitted
per behavioral region from three real charging corpora---ACN-Data, EV~WATTS,
and ElaadNL---with fit quality and provenance recorded on every value; SoC
channels are explicitly modeled priors made consistent with observed energy,
never presented as measurements. Third, generation is \emph{reproducible}: a
scenario configuration and a single integer seed regenerate any dataset
bitwise, and every run emits a provenance manifest. We quantify
representativeness against real data (ASHRAE Guideline~14 building-load
fidelity versus ComStock and the Building Data Genome~2 meters; held-out,
confidence-interval-quantified distributional fidelity versus the calibration
corpora) and demonstrate utility with train-on-synthetic/test-on-real
forecasting that performs on par with training on real data
(\tstr{}/\trtr{} MAE ratio $0.99$ on ACN-Data), together with a cross-cohort
transfer study. We release the generator (MIT), datasets (CC~BY~4.0),
Croissant metadata, a datasheet, sixty benchmark scenario configurations, and
an 18{,}000-sample ten-building reference corpus.
