\section{Related Work}
\label{sec:related}

We situate \generator{} against five bodies of work: the demand-side V2B
methods that consume coupled data; the real EV-charging datasets that
motivate generation; the building-energy corpora and simulators we use as
physical ground truth; the statistical and deep-generative approaches to
synthesizing charging and load data; and the evaluation and documentation
standards for synthetic data. Table~\ref{tab:related} summarizes where we
differ.

\paragraph{V2B/V2G methods need coupled data.}
A large literature develops optimization and learning methods for smart
charging, vehicle-to-grid, and vehicle-to-building coordination---scheduling
charging against time-of-use tariffs and demand charges, using parked fleets
for building peak shaving, and co-optimizing storage and on-site
PV~\owed{cite: 1--2 V2G/V2B optimization or control surveys}. These methods
are developed and compared on data that couples building load, charging
sessions, tariffs, and distributed energy resources on a common clock.
Because such coupled data is rarely available, evaluations often stitch
together a charging dataset from one source, a load profile from another, and
a synthetic tariff, with no guarantee that the channels are mutually
consistent. \generator{} targets exactly this gap: a coherent, controllable,
multi-channel instance generator for the problems these methods solve.

\paragraph{Real EV-charging datasets.}
The public charging corpora are few and site-specific. ACN-Data
\citep{lee2019acn} provides workplace sessions from three California sites
with driver-entered energy requests; ElaadNL releases anonymized
public-charging transactions from the Netherlands \citep{elaadnl2020}; the
DOE-funded EV~WATTS program published a large multi-venue U.S. evaluation
dataset \citep{evwatts2023}; and the earlier INL EV Project documented a
2011--2013 residential fleet \citep{inl2015evproject}. Each is confined to a
fixed set of venues and infrastructures, none couples building-side load, and
critically, none records battery state of charge---charging equipment meters
delivered energy, not the battery. These corpora anchor our calibration
(\S\ref{sec:calibration}); their coverage and access limits, and the absent
SoC channel, are what generation is meant to overcome.

\paragraph{Building-energy data and simulation.}
On the building side, substantial public resources exist and we consume them
as \emph{ground truth} rather than as competitors. NREL's ComStock provides
calibrated end-use load profiles for the U.S. commercial building stock
\citep{parker2023comstock}, and the Building Data Genome~2 project publishes
metered data from over a thousand non-residential buildings
\citep{miller2020bdg2}; both serve as validation references
(\S\ref{sec:loadfidelity}). Our building channel is produced by physics-based
simulation: EnergyPlus \citep{crawley2001energyplus} driven by the DOE
prototype building models \citep{pnnl_prototypes}, with on-site PV modeled by
the PVWatts algorithm \citep{dobos2014pvwatts}. Keeping simulation
(generation) and metered corpora (evaluation) in separate roles is a
deliberate design choice that avoids validating a model against itself.

\paragraph{Statistical and simulation models of charging behavior.}
The classical approach to synthetic charging demand fits parametric
distributions to observed behavior---arrival times, dwell (connection)
durations, and energy per session---often with Gaussian-mixture or related
families, and composes them into aggregate load
models~\owed{cite: 1--2 statistical EV-load / GMM charging-behavior papers}.
Charging-infrastructure simulators embed such models: ACN-Sim includes a
generative session model fitted to ACN-Data \citep{lee2021acnsim}, and
ElaadNL distributes simulation profiles derived from its transactions
\citep{elaadnl2020}. \generator{} is in this lineage but extends it on three
axes: it fits distributions \emph{per behavioral region} rather than
per site aggregate, links arrival and dwell with an explicit copula, and
calibrates the same parametric interface across multiple independent corpora,
while embedding the behavioral model inside a physical building simulation so
that the charging and load channels are jointly consistent.

\paragraph{Deep generative models for tabular and time-series data.}
A parallel line learns the joint distribution of a dataset with deep
generative models---recurrent and conditional GANs
\citep{esteban2017rgan,yoon2019timegan} and, more recently, score-based
diffusion models for time series \citep{tashiro2021csdi}, with domain
variants for energy load and charging
data~\owed{cite: optional energy/load GAN or diffusion paper}. These models
can capture rich dependence at a single site, but they imitate one observed
distribution without exposing scenario controls (one cannot relocate a
learned site to a new climate or resize its fleet), provide no mechanism for
physical consistency across coupled channels, and are not reproducible or
auditable at the level of individual values. We deliberately trade the
expressiveness of a learned joint density for a parametric, copula-coupled,
physically-grounded model that is controllable, per-value auditable, and
bitwise reproducible; \S\ref{sec:representativeness}--\S\ref{sec:utility}
quantify what this trade costs and returns.

\paragraph{Evaluating and documenting synthetic data.}
We adopt the two-sided evaluation now standard for synthetic data:
distributional fidelity against held-out real data, and downstream utility
via the train-on-synthetic/test-on-real (TSTR) protocol introduced for
medical time series \citep{esteban2017rgan}. For building-load fidelity we
use the calibration metrics of ASHRAE Guideline~14 \citep{ashrae2014g14}
($\cvrmse{}$, $\nmbe{}$), the accepted standard for comparing simulated to
metered building energy. For documentation and discoverability we follow
Datasheets for Datasets \citep{gebru2021datasheets} and the Croissant
machine-readable metadata format \citep{akhtar2024croissant}.

\begin{table}[t]
\caption{Positioning. \generator{} is the only approach that is coupled
across channels, physically grounded, calibrated to multiple real corpora,
and bitwise reproducible with per-value provenance.}
\label{tab:related}
\centering\small
\begin{tabular}{@{}lcccc@{}}
\toprule
 & Coupled & Physically & Multi-corpus & Reproducible \\
Approach & channels & grounded & calibrated & + provenance \\
\midrule
Real charging datasets & no & --- & --- & --- \\
Building corpora (ComStock/BDG2) & no & yes & --- & partial \\
Charging simulators (ACN-Sim) & no & no & single & partial \\
Deep generative (GAN/diffusion) & rarely & no & single & no \\
\textbf{\generator{}} & \textbf{yes} & \textbf{yes} & \textbf{yes} & \textbf{yes} \\
\bottomrule
\end{tabular}
\end{table}
