\section{Representativeness}
\label{sec:representativeness}

The generators category requires representativeness to be quantified. We
evaluate the building channel against independent real meter corpora, the
behavioral channel against the calibration corpora under a held-out protocol
with bootstrap confidence intervals, and the DER channels against an external
reference implementation. All evaluations use the clean noise profile and raw
(non-peak-normalized) simulated magnitudes.

\subsection{Building load versus real meters}
\label{sec:loadfidelity}

We compare generated load against two independent references: NREL ComStock
end-use load profiles (climate zones 5B, 3B, 4A, 6A) and nineteen real meters
from the Building Data Genome~2 corpus, matched by archetype and size.
Following ASHRAE Guideline~14 we report $\cvrmse{}$ and $\nmbe{}$, together
with normalized load-shape correlation, peak-hour error, and load factor.
Generated \emph{shapes} track the real stock well: shape correlation ranges
$0.71$--$0.94$ across archetypes and peak-hour error is at most three hours.
Absolute intensity reflects the single-prototype scope: four of five
archetypes sit 37--54\% below the stock-average ComStock intensity---as
expected when one code-compliant 2019 prototype represents a heterogeneous
building stock---while the large-office archetype sits 27\% above
($\nmbe{} = -27.1\%$). We report these per archetype (Table~\ref{tab:g14})
rather than in aggregate, and return to the implication in
\S\ref{sec:limitations}.

\begin{table}[t]
\caption{Building-load fidelity versus ComStock (ASHRAE G14 metrics) per
archetype: mean generated vs.\ reference power, $\cvrmse{}$, $\nmbe{}$
(positive = generator under-predicts), weekday shape correlation, and
peak-hour error.}
\label{tab:g14}
\centering\small
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
Archetype & gen kW & ref kW & $\cvrmse{}$\% & $\nmbe{}$\% & shape $r$ & $\Delta$pk h \\
\midrule
office/small & 4.1 & 8.0 & 56.7 & $+49.1$ & 0.71 & 1 \\
office/med & 43.3 & 68.7 & 47.2 & $+37.0$ & 0.91 & 2 \\
office/large & 773.1 & 608.3 & 43.7 & $-27.1$ & 0.94 & 3 \\
retail/med & 27.9 & 60.6 & 59.3 & $+54.0$ & 0.91 & 1 \\
retail/large & 21.5 & 36.6 & 51.6 & $+41.2$ & 0.87 & 1 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Behavioral fidelity: held-out and interval-quantified}
\label{sec:behfidelity}

For each calibrated population we generate sessions across seeds and compare,
region by region and variable by variable, against the source corpus: mean
absolute error of the mean ($|\Delta\mu|$), the two-sample KS statistic, and
the Wasserstein-1 distance, with the arrival--dwell copula compared by
Spearman correlation gap. With thousands of sessions per cell the KS
$p$-value is uninformative; we therefore judge by effect size and quantify
sampling uncertainty by a seeded percentile bootstrap ($B{=}1000$) over
source sessions, reported as 95\% intervals on every cell. Aggregate
results over the 36 region$\times$variable cells of the six evaluated
sources: mean $|\Delta\mu|$ of $0.44$\,h; the worst well-sampled cell
(arrival in the largest ACN region) has $\ks = 0.222\ [0.209, 0.235]$, and
the global worst is a 41-user single-site cell at $\ks = 0.239$ with a
correspondingly wide interval $[0.146, 0.385]$; maximum copula $\rho$-gap
$0.226$.

Held-out fidelity is evaluated under a \emph{family-matched} protocol:
distributions are refitted on a training split of drivers using the same
family-selection rule that calibration ships (including mixture selection)
and scored against the unseen split. We report this protocol because an
earlier single-family variant understated degradation; under the matched
protocol the median degradation is
$\ks_{\text{holdout}} - \ks_{\text{train}} = 0.064$, and the full per-cell
table (appendix) discloses the outliers: $+0.425$ in a cell with only 62
held-out sessions, where the deterministic driver split induces cohort
shift that small samples cannot average out, but also $+0.372$ in a
well-sampled cell ($n_{\text{test}} = 1{,}386$), which cannot be attributed
to sampling noise and indicates genuine within-region driver heterogeneity.
We read the held-out results as honest evidence of moderate generalization:
typical cells transfer with single-digit-percent KS inflation; the failures
are localized and disclosed, mostly---but not exclusively---where data is
thin.

A regenerated ablation isolates the two calibration decisions
(fitted-CDF-versus-source KS, the fitter's own quality metric): replacing the
pooled arrival fit broadcast to all regions with per-region fits reduces the
largest ACN region's arrival KS from $0.196$ to $0.040$; admitting mixture
families improves mean ACN arrival KS from $0.100$ to $0.042$, and across
all fourteen cells where the selection rule chose a mixture, from $0.134$ to
$0.035$ --- capturing the bimodality of Fig.~\ref{fig:arrival}. Dwell
mixtures fire more conservatively (four of sixteen cells; $0.127$ to
$0.102$).

\subsection{DER channels}
\label{sec:derfidelity}

The PV model is deterministic physics, so we validate it against an external
reference implementation---NREL's PVWatts~v8 via the SAM SDK---under
identical configuration and the \emph{same} weather file, eliminating
weather-source confounds. Annual energy agrees to $+1.27\%$ (ours
164.5\,MWh vs.\ 162.4\,MWh for a 100\,kW$_{\mathrm{DC}}$ system); every
month agrees within $\pm 2.6\%$; hourly agreement is well inside ASHRAE
Guideline~14 calibration tolerances ($\cvrmse{} = 15.1\%$,
$\nmbe{} = +1.3\%$, Pearson $r = 0.994$), and a lag scan confirms exact
time-axis alignment. A derate-equalized secondary run isolates the pure
physics difference (isotropic vs.\ Perez transposition, NOCT thermal model)
at $-2.8\%$; both readings sit comfortably under the 5\% acceptance gate.
DR event \emph{timing} follows program rules by construction (season,
notification lead, caps). Event \emph{magnitudes} were audited against
primary program sources: the BIP range is tariff-derived (the 100\,kW minimum
load reduction and the 85\%-of-peak firm-service-level bound are taken
verbatim from the utility tariff) and the CBP range is consistent with
per-account impacts in the statewide program evaluations (means of
13--39\% of reference load), while ELRP per-site magnitudes are redacted in
every public evaluation and our range is therefore an explicitly stylized
prior. Section~\ref{sec:limitations} states the resulting scope, and the
grounding memorandum with citations ships with the artifact.
