\section{Utility: Train on Synthetic, Test on Real}
\label{sec:utility}

Representativeness alone does not establish that a generator is useful; the
generators category asks for demonstrated utility. We adopt the
train-on-synthetic/test-on-real protocol: a forecasting model is trained
either on generated data ($\tstr{}$) or on real training data ($\trtr{}$) and
evaluated on the same held-out real test set; the ratio $\tstr{}/\trtr{}$ of
test errors measures how much is lost by training synthetically (parity is
$1.0$; below $1.0$ the synthetic-trained model generalizes better).

\paragraph{Task and regimes.}
Short-horizon charging-demand forecasting on the real corpus, in two feature
regimes: \emph{lagged} (recent-history features, the standard setting) and a
\emph{calendar-only} probe (time-of-day and day-of-week features only), which
isolates whether the generator reproduces the demand's structural rhythm
rather than merely its autocorrelation. Because a synthetic site's absolute
scale is a scenario choice (fleet size, charger count) rather than a fitted
quantity, we additionally report a \emph{unit-mean-normalized} variant that
scales each cohort by its training-split mean, separating load-\emph{shape}
transfer from magnitude transfer.

\paragraph{Same-cohort transfer (ACN-Data).}
Training on \generator{} output calibrated to the ACN workplace cohort
transfers at parity: $\tstr{}/\trtr{}$ of $0.99\times$ (MAE) and $0.92\times$
(RMSE) in the lagged regime. In the calendar-only probe the synthetic-trained
model \emph{outperforms} the real-trained one ($0.57\times$/$0.79\times$):
the generated sessions present the workplace rhythm with less measurement
idiosyncrasy than the limited real training split---a pattern consistent with
synthetic data acting as a regularizer when features are weak.

\paragraph{Cross-scale transfer (ElaadNL).}
The ElaadNL experiment is deliberately harder: the matched synthetic scenario
is a single 20-vehicle building, while the real series aggregates a
network-scale cohort (${\sim}3{,}400$ vehicle identifiers; 481\,kW observed
peak versus 26\,kW synthetic). Shape transfer again reaches parity---the
calendar-only, unit-mean-normalized ratio is $1.02\times$ (MAE) and
$1.03\times$ (RMSE)---while lagged raw-magnitude transfer degrades to
$7.4\times$/$6.2\times$: a lag-feature model trained at building scale cannot
extrapolate to a fleet two orders of magnitude larger, and a 20-vehicle
aggregate is intrinsically spikier than a 3{,}400-vehicle one. We report both
rows (Table~\ref{tab:tstr}) and read them as a \emph{scale-shift} result: the
calibrated behavioral shape carries across cohorts and continents, whereas
absolute-magnitude transfer requires matching the scenario's fleet scale to
the target---which is precisely the parameter the generator exposes.\footnote{
An earlier run of this experiment paired the ElaadNL test series with an
ACN-calibrated scenario owing to a default-argument defect in the evaluation
harness; the defect is fixed, the superseded artifact is retained in the
repository as evidence, and all numbers reported here use the matched
ElaadNL-calibrated scenario.}

\begin{table}[t]
\caption{TSTR/TRTR error ratios ($1.0$ is parity; lower favors the
synthetic-trained model). ElaadNL rows are a deliberate cross-scale transfer
(20-vehicle synthetic building vs.\ network-scale real aggregate).}
\label{tab:tstr}
\centering\small
\begin{tabular}{@{}llcc@{}}
\toprule
Corpus & Regime & MAE ratio & RMSE ratio \\
\midrule
ACN-Data & lagged, raw & 0.99 & 0.92 \\
ACN-Data & calendar-only, raw & 0.57 & 0.79 \\
ElaadNL & lagged, raw & 7.38 & 6.16 \\
ElaadNL & lagged, normalized & 4.19 & 3.72 \\
ElaadNL & calendar-only, raw & 1.32 & 1.31 \\
ElaadNL & calendar-only, normalized & \textbf{1.02} & \textbf{1.03} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Distribution-shift benchmarks.}
Because cohorts are first-class configurations, shift experiments come free:
train on the US-workplace cohort and test on the EU-public cohort---or on the
fixture-calibrated 2011-era residential cohort---holding every other channel
fixed. We release these pairs as benchmark tasks; the ElaadNL cross-scale
result above is the first datapoint.
