\section{Limitations and Ethics}
\label{sec:limitations}

We list the limitations we know of, each with its evaluation consequence.

\paragraph{Single-climate-zone building physics.}
All prototype models ship in one climate zone (Denver, CZ~5B), while tariffs
and weather span nine sites. Load-shape fidelity was validated against
ComStock across four climate zones (\S\ref{sec:loadfidelity}), but absolute
intensities inherit the single-prototype scope, including the per-archetype
EUI deviations reported there (four archetypes 37--54\% below stock average;
large office 27\% above). Claims about absolute energy magnitudes across
climates should be scoped accordingly; shipping additional climate-zone
prototypes is mechanical future work.

\paragraph{SoC channels are model priors.}
Restated once more because it is the release's most important caveat: no
source measures SoC; both SoC channels follow the explicit reconstruction
contract of \S\ref{sec:soc}.

\paragraph{Calibration scope.}
The ACN region grid predates the re-anchoring procedure applied to ElaadNL
and retains its original geometry; the consistency metric $\kapcons$ is
origin-dependent; and the Gaussian copula was chosen for closed-form
inversion although a Frank copula fits the arrival--dwell dependence better
in several regions --- the transform bias is documented in the repository.
Held-out dwell fidelity degrades in three cells (up to $+0.29$ KS), disclosed
in Table~\owed{2}. Arrival tails that approach uniformity are approximated by
truncated mixtures. The INL cohort is a labeled fixture, not a fitted corpus.

\paragraph{DER channels.}
PV is validated against an external reference implementation
(\S\ref{sec:derfidelity}) but not against metered arrays. DR magnitude
ranges are tariff-derived for BIP and evaluation-consistent for CBP, but the
uniform \emph{shape} of the magnitude distribution is a modeling choice
(public evaluations report means, not distributions), and the ELRP range is
an explicitly stylized prior because per-site nominations are redacted in
every public evaluation. Our audit also found second-order timing
simplifications --- notification leads and event caps are conservative
relative to the tariffs, and the sampler's evening window ends one hour
before the 8--9\,p.m.\ slot in which recent real ELRP events ran --- which
we record as tracked issues rather than silently correct after the
evaluation freeze. Tariff prices are descriptor constants representative of
the named utilities rather than imported rate schedules; mapping to a rate
database is future work.

\paragraph{Validation tolerances.}
Two share-consistency checks (negotiation-type and region shares) are
enforced as soft advisories with a sample-size-aware tolerance rather than
the original strict specification; all physical and structural invariants
remain hard.

\paragraph{Ethics and misuse.}
The release contains no personal data: every driver, vehicle, and session is
synthetic by construction, and calibration used only public or
access-approved corpora under their terms, aggregated to distribution
parameters (no record-level content is redistributed). The residual risks we
see are epistemic rather than privacy-related: results obtained on synthetic
data may be over-trusted if the representativeness scope above is ignored,
and the SoC contract may be mistaken for measurement despite labeling. We
mitigate both by prominent documentation (datasheet, this section) and by
shipping the evaluation harnesses so that fidelity claims are re-checkable.
A fuller statement accompanies the artifact.
